Multi-armed bandit \mengyan{(Bayesian?)} optimisation\\ of bacterial Ribosome Binding Site

### 2021-11-15 paper/main.tex

Figure \ref{fig: Swarmplot and Quantplot}B shows the same results but divided into quantiles where the specific point for a given group shows the highest TIR for that quantile.
The gradual increase for all quantiles can be observed for all Bandit groups, suggesting that the algorithms have a better understanding of the experimental space given more data.
The decreased result in the 0.9th quantile compared to the maximum value for the Bandit 3 group can be attributed to the increased emphasis on exploitation that has been set for that round compared to others.
We see this effect in Figure \ref{fig: Swarmplot and Quantplot}C (with details shown in Figure  \ref{fig:exploitationvsexplorationdetail}), where we coloured the data points for Bandit 1-3 groups according to their relative exploration - exploitation affinity.
Those with a high predicted mean are coloured blue and represent exploitation, those coloured red are with high predicted uncertainty and represent exploration.
We can see that the RBSs with high TIRs tend to come from exploitation of the design space, whereas the explorative points give relatively low TIRs, but expand our knowledge of the unknown part of the design space.\\

@@

Another interesting characteristic uncovered by our research is the perceived editing distance between two sequences required for  improvement in the TIR when the given RBS' TIR is already high. 
We define the edit distance as Hamming distance, that is, how many positions have to be changed to get from one sequence to the other (Hamming distance of 0 means that the sequences are identical and 6 means that they are two completely different sequences).
Figure \ref{fig:Library characteristics}B shows the edit distance is required for positive change in TIR for an RBS with TIR $>0.75$.
For RBSs with high TIRs ($>1$), the minimum distance that is required to increase the TIR is 2, with edit distances between 2 and 5 giving similar results.
For RBSs with medium TIRs ($<1$), a distance of 1 is enough to produce a meaningful increase in TIR.
This means that as the TIRs of examined RBSs increase, exploring sequences which are more dissimilar to the current candidates tends to give more meaningful improvement. 
As long as this does not impact targeted methods like machine learning-guided design, it does imply that the low rate of natural mutations will be very slow to explore more dissimilar sequences on such a short distance \cite{Lee2012}, which indicates that methods like Adaptive Laboratory Evolution may not be able to find very strong RBSs with a limited budget.  
In other words, because the examined sequence is relatively short (6 bp in a wider 20 bp context) the time required to accumulate 2 or more changes in the RBS region required for meaningful increase in TIR might be prohibitively long.
In such cases, a directed process, like the one described here, should be strongly encouraged.
This observation is in line with approaches seen in other disciplines, e.g. protein engineering, where more directed changes yield better results than wide random changes \cite{Jackel2008}.\\

@@

\section{Discussion}

>>>>

Figure \ref{fig: Swarmplot and Quantplot}B shows the same results but divided into quantiles where the specific point for a given group shows the highest TIR for that quantile.
The gradual increase for all quantiles can be observed for all Bandit groups, suggesting that the algorithms have a better understanding of the experimental space given more data.
The decreased result in the 0.9th quantile compared to the maximum value for the Bandit 3 group can be attributed to the increased emphasis on exploitation that has been set for that round compared to others.
We see this effect in Figure \ref{fig: Swarmplot and Quantplot}C (with details shown in Figure  \ref{fig:exploitationvsexplorationdetail}), where we coloured the data points for Bandit 1-3 groups according to their relative exploration - exploitation affinity.
Those with a high predicted mean are coloured blue and represent exploitation, those coloured red are with high predicted uncertainty and represent exploration.
\hl{Since we expect that an RBS sequence chosen at random will have low TIR
(as shown by UNI and PPM), this implies that most of the exploration will result in low TIR.
Our results confirm that
RBSs with high TIRs tend to come from exploitation of the design space,
whereas the exploration points give relatively low TIRs. Note that the exploration is necessary to expand our knowledge of unknown parts of the design space.}\\

@@

Another interesting characteristic uncovered by our research is the perceived editing distance between two sequences required for  improvement in the TIR when the given RBS' TIR is already high.
We define the edit distance as Hamming distance, that is, how many positions have to be changed to get from one sequence to the other (Hamming distance of 0 means that the sequences are identical and 6 means that they are two completely different sequences).
Figure \ref{fig:Library characteristics}B shows the edit distance is required for positive change in TIR for an RBS with TIR $>0.75$.
For RBSs with high TIRs ($>1$), the minimum distance that is required to increase the TIR is 2, with edit distances between 2 and 5 giving similar results.
For RBSs with medium TIRs ($<1$), a distance of 1 is enough to produce a meaningful increase in TIR.

This means that as the TIRs of examined RBSs increase, exploring sequences which are more dissimilar to the current candidates tends to give more meaningful improvement. 
As long as this does not impact targeted methods like machine learning-guided design, it does imply that the low rate of natural mutations will be very slow to explore more dissimilar sequences on such a short distance \cite{Lee2012}, which indicates that methods like Adaptive Laboratory Evolution may not be able to find very strong RBSs with a limited budget.  
In other words, because the examined sequence is relatively short (6 bp in a wider 20 bp context) the time required to accumulate 2 or more changes in the RBS region required for meaningful increase in TIR might be prohibitively long.
In such cases, a directed process, like the one described here, should be strongly encouraged.
This observation is in line with approaches seen in other disciplines, e.g. protein engineering, where more directed changes yield better results than wide random changes \cite{Jackel2008}.\\

@@

\section{Discussion and Conclusion}

### 2021-11-15 paper/supplementary.tex

A Gaussian process is specified by its mean function and \hl{covariance} function as $f(\mathbf{x}) \sim \mathcal{G} \mathcal{P}\left(\mu(\mathbf{x}), k\left(\mathbf{x}, \mathbf{x}^{\prime}\right)\right)$.
We consider the case where the observations are noisy, i.e. $(X, \mathbf{y}) = \{(\mathbf{x}_i, y_i)| i = 1, \dots, n\}$, where $y_i = f(\mathbf{x}_i) + \epsilon$ with $\epsilon \sim \mathcal{N}(0, \alpha^2)$. 
The Gaussian noise is independent identically distributed, and the \hl{covariance of the prior on the} noisy observations is then $\operatorname{cov}\left(y_{p}, y_{q}\right)=k\left(\mathbf{x}_{p}, \mathbf{x}_{q}\right)+\alpha^{2} \delta_{p q}$,
where $\delta_{pq}$ is a Kronecker delta which is one if $p = q$ and zero otherwise.
It is equivalent to a diagonal matrix $\alpha^2 I$ \hl{added} on the kernel matrix evaluated on the training points.

For $n_\ast$ test points $X_\ast$, we assume the prior over the functions values as a random Gaussian vector $\mathbf{f}_\ast \sim \mathcal{N}(\mathbf{0}, K(X_\ast, X_\ast))$.
Then the joint distribution of the observed target values and the function values at the test points under the prior as 
\begin{align}
    \left[\begin{array}{l}\mathbf{y} \\ \mathbf{f}_{*}\end{array}\right] \sim \mathcal{N}\left(\mathbf{0},\left[\begin{array}{cc}K(X, X)+\alpha^{2} I & K\left(X, X_{*}\right) \\ K\left(X_{*}, X\right) & K\left(X_{*}, X_{*}\right)\end{array}\right]\right)
\end{align}
where $K(X, X_\ast)$ denotes the $n \times n_\ast$ covariance/Kernel matrix evaluated at all pairs of training and testing points, similarly for other kernel matrices.
Then the posterior of the test points (i.e. predictive distributions) is given by the conditional distribution $\mathbf{f}_\ast | X, \mathbf{y}, X_\ast \sim \mathcal{N}(\bar{\mathbf{f}}_\ast, cov(\mathbf{f}_\ast))$, where
\begin{align}
   \overline{\mathbf{f}}_{*} & \triangleq \mathbb{E}\left[\mathbf{f}_{*} \mid X, \mathbf{y}, X_{*}\right]=K\left(X_{*}, X\right)\left[K(X, X)+\alpha^{2} I\right]^{-1} \mathbf{y} \\
   \label{Eq: predicted variance}
   \operatorname{cov}\left(\mathbf{f}_{*}\right) &=K\left(X_{*}, X_{*}\right)-K\left(X_{*}, X\right)\left[K(X, X)+\alpha^{2} I\right]^{-1} K\left(X, X_{*}\right) 
\end{align}
For noisy test targets $\mathbf{y}_\ast = f(\mathbf{x}_\ast) + \epsilon$ with $\epsilon \sim \mathcal{N}(0, \alpha^2)$, we can compute the predictive distribution by adding $\alpha^2 I$ to the variance term $cov(\mathbf{f}_\ast)$ in Eq. (\ref{Eq: predicted variance}),
\hl{
i.e. $\overline{\mathbf{y}}_{*} = \overline{\mathbf{f}}_{*}$, $\operatorname{cov}\left(\mathbf{y}_{*}\right) = \operatorname{cov}\left(\mathbf{f}_{*}\right) + \alpha^2 I$.
}

@@

\begin{itemize}
    \item \textit{Spectrum Kernel.}
    \begin{align}
        k_\ell^{\text{Spec}}(\mathbf{x}, \mathbf{x}^\prime) =\left\langle\phi_{\ell}^{\mathrm{Spec}}(\mathbf{x}), \phi_{\ell}^{\mathrm{Spec}}\left(\mathbf{x}^{\prime}\right)\right\rangle = \phi_{\ell}^{\mathrm{Spec}}(\mathbf{x})^T \phi_{\ell}^{\mathrm{Spec}}\left(\mathbf{x}^{\prime}\right).
    \end{align}
     where $\mathbf{x}, \mathbf{x}^\prime$ are two RBS sequences in $\mathcal{D}$ over an alphabet $\Sigma$. We denote the number of letters in the alphabet as $|\Sigma|$. 
     \hl{
     In our case, $\Sigma = \{A,C,G,T\}$ and $|\Sigma| = 4$.
     }
    $\phi_{\ell}^{\mathrm{spec}}(\mathbf{x})$ maps the sequence $\mathbf{x}$ into a $|\Sigma|^\ell$ dimensional feature space, where each dimension is the count of the number of one of the $|\Sigma|^\ell$ possible strings $s$ of length $\ell$. 
    \hl{
    For example, if $\mathbf{x} = ACACAG$ and $\ell = 3$, then $\phi_{\ell}^{\mathrm{spec}}(\mathbf{x})$ maps $\mathbf{x}$ into $4^3$ dimensional feature space, where each dimension corresponds to $AAA, AAC, AAT, AAG, ACA, ..., TTT$. Among those, the dimension corresponds to $ACA, CAC, CAG$ are 2,1,1 and others are 0. 
    }
    Let $X, X^\prime$ be two metrics which include $n$ sequences, and $\Phi_\ell^{Spec}(X) \in \mathbb{R}^{n \times |\Sigma|^{\ell}}$, then the spectrum kernel over metrics is 
    \begin{align}
         K_\ell^{\text{Spec}}(X, X^\prime) = \Phi_{\ell}^{\mathrm{Spec}}(X) \Phi_{\ell}^{\mathrm{Spec}}\left(X^{\prime}\right)^T.
    \end{align}

@@

Here we consider two approaches for kernel normalisation: centering and unit norm. 
We will show how to convert the normalisation in terms of feature vectors to normalisation in terms of kernel matrices. 
As defined before, consider $\mathbf{x}, \mathbf{x}^\prime$ are two RBS sequences in $\mathcal{D}$ over an alphabet $\Sigma$.
We denote $\phi(\mathbf{x})$ as a column feature vector of sequence $\mathbf{x}$, 
where a feature function $\phi: \mathbf{x} \rightarrow \mathbb{R}^d$,
\hl{with $d$ as the dimension of features.
One example of $\phi$ can be $\phi_\ell^{spec}(\mathbf{x})$ in the spectrum kernel.
Recall the corresponding kernel can be defined as $k(\mathbf{x}, \mathbf{x}^\prime) = \phi(\mathbf{x})^T \phi(\mathbf{x}).$
}
Assume there is total of $n$ sequences in the data $X$ ($n'$ sequences in the data $X'$). 
We illustrate centering and unit norm normalisation below.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[scale=0.4]{plots/Supplementary/core_vs_noncore.pdf}
    \caption{\textbf{Comparison of base change impact on TIR in core versus non-core region.} 
    \hl{The core region is highlighted in light green and the lines are rolling averages (in this case mean of the 5 points centred over the indicated position) for each base.}
    The top dotted line shows the TIR for the benchmark sequence, where dots represent a change at a given position to a given base, which is colour coded.
    \hl{Since only changes from the original base at each position are shown, the dotted lines start and end at different positions depending on how many changes to the respective base are at positions adjacent to the indicated one.}
    The value of Welch's t-test between the mean TIR in core and non-core groups is -4.8780 with p-value $<$ 0.0001 and 34 degrees of Freedom.}
    \label{fig:core_vs_noncore}
\end{figure}

@@

\begin{figure}[!ht]
   \centering
    \includegraphics[scale=0.35]{plots/Supplementary/proj_scatter_abc1_FF_0.pdf}
    \includegraphics[scale=0.35]{plots/Supplementary/proj_scatter_abc1_FF_1.pdf}
    \includegraphics[scale=0.35]{plots/Supplementary/proj_scatter_abc1_FF_2.pdf}
   \caption{\textbf{Exploration-Exploitation scores illustration.} The orange points show the predicted STD and TIR (with the setting of Figure \ref{fig: Scatterplot}) for test data points (recommendations in Round 1-3). 
   \hl{
   We project the orange points to the diagonal line crossing (0,1) and (1,0). We colour those projected points using RdBu palette, which are exploration-exploitation colours/scores shown in Figure \mbox{\ref{fig: Swarmplot and Quantplot}C}.
   The hued red colour corresponds to points that are predicted to have high STD (uncertainty), which are recommended for \textit{exploration}; the hued blue colour corresponds to points that are predicted to have high TIR, which are recommended for \textit{exploitation}.}}
   \label{fig:exploitationvsexplorationdetail}
\end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[scale = 0.35]{plots/Supplementary/scatter_bc1_TTF_0.pdf}
    \includegraphics[scale = 0.35]{plots/Supplementary/scatter_abc1_TT_1.pdf}
    \includegraphics[scale = 0.35]{plots/Supplementary/scatter_abc1_TT_2.pdf}
    % \includegraphics[scale = 0.4]{plots/Supplementary/scatter_abc1_TT_3.pdf}
    \caption{\textbf{Predictions in design pipeline in Round 1-3.} For Round 1, the kernel matrix is normalised based on known RBS sequences in Round 0. For Round 2-3, the kernel matrix is normalised based on all RBS sequences in the design space.
    \hl{
    Compared to the results shown in Figure \mbox{\ref{fig: Scatterplot}}, here we have applied kernel normalisation shown in Section \mbox{\ref{supp: Normalisation of Kernel}}. Although the $R^2$ scores decrease a lot compared with Figure \mbox{\ref{fig: Scatterplot}}, the Spearman correlation remains similar.
    }
    }
    \label{fig:scatter abc1 TT.}
\end{figure}

@@

\begin{figure}[!ht]
   \centering
    \includegraphics[scale=0.4]{plots/Supplementary/SDhist.pdf}
   \caption{\textbf{Histogram of standard deviations.} \hl{
   For each RBS sequence, we tested 6 biological replicates. This plot shows the histogram of the STD of raw TIR values of the 6 replicates for each RBS sequence. }}
   \label{fig: SDhist}
\end{figure}

>>>>

A Gaussian process is specified by its mean function and covariance function as $f(\mathbf{x}) \sim \mathcal{G} \mathcal{P}\left(\mu(\mathbf{x}), k\left(\mathbf{x}, \mathbf{x}^{\prime}\right)\right)$.
We consider the case where the observations are noisy, i.e. $(X, \mathbf{y}) = \{(\mathbf{x}_i, y_i)| i = 1, \dots, n\}$, where label $y_i = f(\mathbf{x}_i) + \epsilon$ with $\epsilon \sim \mathcal{N}(0, \alpha^2)$. 
The Gaussian noise is independent identically distributed, and the covariance of the prior on the noisy observations is then $\operatorname{cov}\left(y_{p}, y_{q}\right)=k\left(\mathbf{x}_{p}, \mathbf{x}_{q}\right)+\alpha^{2} \delta_{p q}$,
where $\delta_{pq}$ is a Kronecker delta which is one if $p = q$ and zero otherwise.
It is equivalent to a diagonal matrix $\alpha^2 I$ added on the kernel matrix evaluated on the training points.

For $n_\ast$ test points $X_\ast$, we assume the prior over the functions values as a random Gaussian vector $\mathbf{f}_\ast \sim \mathcal{N}(\mathbf{0}, K(X_\ast, X_\ast))$.
Then the joint distribution of the observed target values and the function values at the test points under the prior as 
\begin{align}
    \left[\begin{array}{l}\mathbf{y} \\ \mathbf{f}_{*}\end{array}\right] \sim \mathcal{N}\left(
        \left[\begin{array}{cc}
        \bm{\mu}  \\
        \bm{\mu}_\ast
        \end{array}\right],
    \left[\begin{array}{cc}K(X, X)+\alpha^{2} I & K\left(X, X_{*}\right) \\ K\left(X_{*}, X\right) & K\left(X_{*}, X_{*}\right)\end{array}\right]\right)
\end{align}
where
$\bm{\mu}, \bm{\mu}_\ast$ are mean vectors for $\mathbf{y}, \mathbf{f}_{*}$ respectively,
$K(X, X_\ast)$ denotes the $n \times n_\ast$ covariance/Kernel matrix evaluated at all pairs of training and testing points, similarly for other kernel matrices.
Then the posterior of the test points (i.e. predictive distributions) is given by the conditional distribution $\mathbf{f}_\ast | X, \mathbf{y}, X_\ast \sim \mathcal{N}(\bar{\mathbf{f}}_\ast, cov(\mathbf{f}_\ast))$, where
\begin{align}
   \overline{\mathbf{f}}_{*} & \triangleq \mathbb{E}\left[\mathbf{f}_{*} \mid X, \mathbf{y}, X_{*}\right]=
   \bm{\mu}_\ast + K\left(X_{*}, X\right)\left[K(X, X)+\alpha^{2} I\right]^{-1} (\mathbf{y} - \bm{\mu})\\
   \label{Eq: predicted variance}
   \operatorname{cov}\left(\mathbf{f}_{*}\right) &=K\left(X_{*}, X_{*}\right)-K\left(X_{*}, X\right)\left[K(X, X)+\alpha^{2} I\right]^{-1} K\left(X, X_{*}\right) 
\end{align}
For noisy test targets $\mathbf{y}_\ast = f(\mathbf{x}_\ast) + \epsilon$ with $\epsilon \sim \mathcal{N}(0, \alpha^2)$, we can compute the predictive distribution by adding $\alpha^2 I$ to the variance term $cov(\mathbf{f}_\ast)$ in Eq. (\ref{Eq: predicted variance}),
i.e. $\overline{\mathbf{y}}_{*} = \overline{\mathbf{f}}_{*}$, $\operatorname{cov}\left(\mathbf{y}_{*}\right) = \operatorname{cov}\left(\mathbf{f}_{*}\right) + \alpha^2 I$.

@@

\begin{itemize}
    \item \textit{Spectrum Kernel.}
    \begin{align}
        k_\ell^{\text{Spec}}(\mathbf{x}, \mathbf{x}^\prime) =\left\langle\phi_{\ell}^{\mathrm{Spec}}(\mathbf{x}), \phi_{\ell}^{\mathrm{Spec}}\left(\mathbf{x}^{\prime}\right)\right\rangle = \phi_{\ell}^{\mathrm{Spec}}(\mathbf{x})^T \phi_{\ell}^{\mathrm{Spec}}\left(\mathbf{x}^{\prime}\right).
    \end{align}
     where $\mathbf{x}, \mathbf{x}^\prime$ are two RBS sequences in $\mathcal{D}$ over an alphabet $\Sigma$. We denote the number of letters in the alphabet as $|\Sigma|$. 
     In our case, $\Sigma = \{A,C,G,T\}$ and $|\Sigma| = 4$.
    $\phi_{\ell}^{\mathrm{spec}}(\mathbf{x})$ maps the sequence $\mathbf{x}$ into a $|\Sigma|^\ell$ dimensional feature space, where each dimension is the count of the number of one of the $|\Sigma|^\ell$ possible strings $s$ of length $\ell$. 
    For example, if $\mathbf{x} = ACACAG$ and $\ell = 3$, then $\phi_{\ell}^{\mathrm{spec}}(\mathbf{x})$ maps $\mathbf{x}$ into $4^3$ dimensional feature space, where each dimension corresponds to $AAA, AAC, AAT, AAG, ACA, ..., TTT$. Among those, the dimension corresponds to $ACA, CAC, CAG$ are 2,1,1 and others are 0. 
    Let $X, X^\prime$ be two metrics which include $n$ sequences, and $\Phi_\ell^{Spec}(X) \in \mathbb{R}^{n \times |\Sigma|^{\ell}}$, then the spectrum kernel over metrics is 
    \begin{align}
         K_\ell^{\text{Spec}}(X, X^\prime) = \Phi_{\ell}^{\mathrm{Spec}}(X) \Phi_{\ell}^{\mathrm{Spec}}\left(X^{\prime}\right)^T.
    \end{align}

@@

Here we consider two approaches for kernel normalisation: centering and unit norm. 
We will show how to convert the normalisation in terms of feature vectors to normalisation in terms of kernel matrices. 
As defined before, consider $\mathbf{x}, \mathbf{x}^\prime$ are two RBS sequences in $\mathcal{D}$ over an alphabet $\Sigma$.
We denote $\phi(\mathbf{x})$ as a column feature vector of sequence $\mathbf{x}$, 
where a feature function $\phi: \mathbf{x} \rightarrow \mathbb{R}^d$,
with $d$ as the dimension of features.
One example of $\phi$ can be $\phi_\ell^{spec}(\mathbf{x})$ in the spectrum kernel.
Recall the corresponding kernel can be defined as $k(\mathbf{x}, \mathbf{x}^\prime) = \phi(\mathbf{x})^T \phi(\mathbf{x}).$

Assume there is total of $n$ sequences in the data $X$ ($n'$ sequences in the data $X'$). 
We illustrate centering and unit norm normalisation below.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[scale=0.4]{plots/Supplementary/core_vs_noncore.pdf}
    \caption{\textbf{Comparison of base change impact on TIR in core versus non-core region.} 
    The core region is highlighted in light green and the lines are rolling averages (in this case mean of the 5 points centred over the indicated position) for each base.
    The top dotted line shows the TIR for the benchmark sequence, where dots represent a change at a given position to a given base, which is colour coded.
    Since only changes from the original base at each position are shown, the dotted lines start and end at different positions depending on how many changes to the respective base are at positions adjacent to the indicated one.
    The value of Welch's t-test between the mean TIR in core and non-core groups is -4.8780 with p-value $<$ 0.0001 and 34 degrees of Freedom.}
    \label{fig:core_vs_noncore}
\end{figure}

@@

\begin{figure}[!ht]
   \centering
    \includegraphics[scale=0.35]{plots/Supplementary/proj_scatter_abc1_FF_0.pdf}
    \includegraphics[scale=0.35]{plots/Supplementary/proj_scatter_abc1_FF_1.pdf}
    \includegraphics[scale=0.35]{plots/Supplementary/proj_scatter_abc1_FF_2.pdf}
   \caption{\textbf{Exploration-Exploitation scores illustration.} We show the predictions for each sequence from Round 1-3 in orange (with the same settings as Figure \mbox{\ref{fig: Scatterplot}}).
   For a given round all the tested sequences are then projected along the diagonal line crossing (0,1) and (1,0) according to their predicted STD and mean TIR (the higher the predicted mean the closer the point is to the (1,0) coordinate and the higher the predicted STD the closer the point is to the (0,1) coordinate).
   Each point on the diagonal then, corresponds to an orthogonal projection (known as \emph{vector projection}) of an orange point.
   We do this to transform our predictions into a common basis (where the basis is the diagonal) and so by calculating where a given point falls on the diagonal we can show if its mean TIR or STD is higher.
   Finally, we colour those projected points using the RdBu spectrum where the points with high STD (exploration) are shown in red and those with high mean TIR (exploitation) are shown in blue, and these correspond to the points shown in Figure \mbox{\ref{fig: Swarmplot and Quantplot}C}.
   }
   \label{fig:exploitationvsexplorationdetail}
\end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[scale = 0.35]{plots/Supplementary/scatter_bc1_TTF_0.pdf}
    \includegraphics[scale = 0.35]{plots/Supplementary/scatter_abc1_TT_1.pdf}
    \includegraphics[scale = 0.35]{plots/Supplementary/scatter_abc1_TT_2.pdf}
    % \includegraphics[scale = 0.4]{plots/Supplementary/scatter_abc1_TT_3.pdf}
    \caption{\textbf{Predictions in design pipeline in Round 1-3.} For Round 1, the kernel matrix is normalised based on known RBS sequences in Round 0.
    For Round 2-3, the kernel matrix is normalised based on all RBS sequences in the design space.
    Compared to the results shown in Figure \mbox{\ref{fig: Scatterplot}}, here we have applied kernel normalisation described in Section \mbox{\ref{supp: Normalisation of Kernel}}. Although the $R^2$ scores decrease considerably compared with Figure \mbox{\ref{fig: Scatterplot}}, the Spearman correlation remains similar.
    }
    \label{fig:scatter abc1 TT.}
\end{figure}

@@

\begin{figure}[!ht]
   \centering
    \includegraphics[scale=0.4]{plots/Supplementary/SDhist.pdf}
   \caption{\textbf{Histogram of standard deviations.}
   For each RBS sequence, we tested 6 biological replicates. This plot shows the histogram of the STD of raw TIR values of the 6 replicates for each RBS sequence. }
   \label{fig: SDhist}
\end{figure}
